A parametricity-based formalization of semi-simplicial and semi-cubical sets

### 2023-01-21 paper/paper.tex
hinting about how building the n+1-semi-(simplex/cube) is a parametricity translation

@@

>>>>

In particular, the standard augmented $(n+1)$-semi-simplex can be obtained by taking a copy of the standard augmented $n$-semi-simplex serving as the base and glueing on top of it another copy of it lifted by one dimension. In the latter, the color becomes an extra point, the points become lines connecting the points of the base to the extra point and so on.

@@

In particular, the standard $(n+1)$-semi-cube can be obtained by taking two copies of the standard $n$-semi-cube serving as bottom and top face and connecting them by a tube obtained as an other copy of the standard $n$-semi-cube stretched in the new dimension.
